Food-web temporal changes according to changes in species

### 2021-10-15 paper/manuscript.Rmd
Discussion reviewed + add histogram to plots

---
title: "Species richness and biomass temporal trends reveals different assembly processes of food-web in natural fish assemblages " 
author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine (ordre non fixé)
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
  bookdown::word_document2:
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

@@

## Trends of biodiversity needs to be assessed for multiple facets

@@

The documentation of biodiversity trends generally neglect species interactions
although they are fundamentals to ecosystem functioning
[@thebault_food-web_2003; oconnor_general_2016]. In food-webs, empirical and
theoretical studies reported generally that trophic level positively scales to
community biomass [@wang_biodiversity_2018; @danet_species_nodate] (add
mechanisms ?). Trophic level has also been shown to stabilise the temporal
variation of community biomass [@shanafelt_stability_2018;
@danet_species_nodate]. Connectance, which measures the degree of generalism in
a network, was shown to increase robustness to extinction [@dunne_network_2002].
However, the temporal variation of food-web structure is largely unknown
[@kortsch_disentangling_2021]. Food-web temporal variation are often reported
across small time step [warren_spatial_1969; @pecuchet_species_2020;
@kaartinen_high_2012].

@@

In this line, how the temporal changes of community biomasse are related to
temporal changes of species richness can still be question in natural settings,
especially in food-webs. Our knowledge on how the temporal changes of food-web
structure are related  to temporal changes in community biomass and species
richness is almost zero. Our knowledge on the relationships between food-web
structure comes often from comparison of food-web snapshots along spatial
gradient, raising the question of the validity of space for time substitution to
infer consequences of species richness and community biomass on food-web
structure. The increasing amount of availability ecological temporal series
makes possible to assess those questions. Using a standardized monitoring of
fish freshwater communities on the period 1995-2018 and a method of food-web
inference based on allometric relationships and food diet datas, we assessed the
relationships among temporal changes of food-web structure, trends of community
biomass and trends in species richness. We then assessed the validity of space
for time substitution by comparing if temporal relationships display the same
patterns than relationships obtained along spatial gradient.

@@

There was a clear relationship between the size of the communities and their
temporal dynamics. Communities that displayed low community biomass at the
beginning of their monitoring tend to display an biomass increase through time
and reversely. We observed the same pattern for species richness, with
communities that displayed high species richness at the beginning of their
monitoring tend to display a decrease in species richness through time and
reversely.

@@

We modelled the dynamics the temporal trends of food-web structure ($dN$)
in function of the temporal trends of community biomass ($dB$) and species
richness ($dR$) in order to to test the relationship among the temporal dynamics of network
structure from one side and species richness and community biomass from another
side.

@@

In order to control for the uncertainties of the estimated temporal trends, each
temporal trend was weighted by the inverse of the product of the standard errors of the
estimated trends, i.e. slopes for the response and the explicative
variables. We also tested a statistical model taking in account the interaction
between the temporal trends of species richness and community biomass (i.e.
adding $\beta_3dBdR$), the
results are presented in supplementary material (Fig. SXX).

@@

@@

with $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
deviation of the explicative and response variable.

@@

```{r}
class_trends_bm_rich <- rigal_classification %>%
  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
  unnest(classif) %>%
  select(variable, station, direction, acceleration, shape_class) 
res_trends <- class_trends_bm_rich %>%
  filter(acceleration == "constant") %>%
  group_by(variable, direction) %>%
  summarise(n = n()) %>%
  group_by(variable) %>%
  mutate(total = sum(n), percent = n / sum(n) * 100 %>% round(., 2))
```

@@

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table \@ref(tab:rsq)). The spatial models were more performant, with
$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
\@ref(tab:rsq-sp)). Over the station in the dataset, we found that
`r res_trends[res_trends$variable == "log_bm_std", ]$total` stations displayed monotonic trends for biomass. Among them, 
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
were classified stable,
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
decreasing,
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
increasing. Regarding the species richness, we found that
`r res_trends[res_trends$variable == "log_rich_std", ]$total` stations displayed monotonic trends.
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
were classified stable,  
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
as decreasing, and 
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increasing", ]$percent`% increasing.

@@

The temporal trends of connectance was positively linked with the one of
community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), meaning also that both
temporal trends had the same direction in average. That is, the stations where
food-web connectance decreased over time had also community biomass that
decreased over time and reversely. It means that communities that lose biomass
over time, also loses generalist predators and reversely that communities
gaining biomass over time also gain generalist predators. Spatially, we found
also a positive relationship between median connectance and median species
richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observed
significant relationships between the temporal trends of connectance and the one
of species richness (Fig. \@ref(fig:bmr)D) when we found spatially a stong
negative relationship between median connectance and median species richness
($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).

@@

Spatially and temporally, species richness scaled positively with
community biomass. Spatially, this result is in accordance with numerous studies was
already found in streams [@woods_testing_2020; @danet_species_nodate] but also
in grasslands, salt marches and forests [@hector_plant_1999;
@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
works also in time. The positive relationship of species richness on total
biomass might be due to resource use complementarity [@carey_determining_2011],
which is held by niche differentiation [@loreau_biodiversity_1998;
@loreau_partitioning_2001] or to the higher probability of getting high biomass
species with higher species richness [@loreau_biodiversity_2001].

## Biomass temporal dynamics is linked to the top trophic level

We found that the temporal increase of the average trophic level was positively
linked to increase of community biomass in line with previous studies suggesting
that the presence of higher predators can lead to higher community biomass
[@wang_biodiversity_2018; @danet_species_nodate]. Increase of average trophic
level can be associated to either gain of biomass in the highest trophic level
or losses of biomass in the lowest trophic. In our case, such gain or losses of
average trophic level is probably associated to the variations of the presence
of large fishes. The finding that the evenness of biomass, measured by the
pielou, decreased through time as community biomass increased and reversely,
meaning that biomass distribution across species become more even when community
biomass decreased and reversely that biomass distribution across species become
less even when community biomass increased. In the same line, the temporal
trends of community biomass were positively correlated to the temporal trends of
the proportion of piscivorous species and trophic species in the community (Fig.
SXX).

We also found in space that evenness of biomass was positively related to
community biomass while evenness of abundances had no relation (Fig. SXX). It
constrasts with previous studies which found a negative relationship between
biomass and evenness of abundances in marine and plant communities
[@drobner_relation_1998; @maureaud_biodiversityecosystem_2019] or studies that
found more even plant communities in terms of abundances number display higher
community biomass [@wilsey_biodiversity_2000].

We further found that the temporal trends of connectance was positively
linked to that one of community biomass, meaning that connectance increases through
time in a given site when community biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This result is also in accordance with  
theoretical work showing that  higher food-web connectance can result in higher
community biomass [@thebault_food-web_2003]. But it contrasts with previous
results [@poisot_trophic_2013; @danet_species_nodate], highlighting that the
relation between connectance and community biomass may be dependant of assembly
processes at work.

##  Biomass and richness variation are not the same process

In contrasts to the results for the community biomass, the temporal trends of
evenness of biomass was positively related to the temporal trends of species
richness, meaning that as species richness temporally increase, the
distribution of biomass become more even, while temporal trends of evenness of
abondances had no significant relationship with species richness (Fig. SXX).
Those results seem indicate that biomass trends are linked to few big individuals
while richness trends are linked to overall shift in dominance in communities.

Surprinsingly, we found that the temporal trends of connectance was not related to
the one of species richness as found spatially in most empirical food-web
[@dunne_network_2006] and also in the present study. This result suggests that
the structure of food-webs might not be very sensitive to variation of species
richness and that species loss and gain concerns species of low trophic level,
which in turn affect connectance very little. Remarkably, temporal
variations of community biomass and the ones of species richness seem to be
linked to high trophic level in the first while being linked to lower trophic
level in the second. Those results highlight that variations in community
biomass and species richness are linked to different assembly processes and/or
pressures, but it is still an open question.

---
#The temporal trend of the average trophic level had no relationship with the
#one of species richness. It is surprising because one can imagine that loss and
#gain of species would reveal assembly/disassembly mechanisms in terms of trophic
#structure. However, we found that when species richness increases, the
#distribution of biomass and individuals among species become more even in the
#community, meaning that dominance decrease.
---

@@

While space for time works for variation of community biomass, it is less clear
for the variation of species richness. Indeed, it was not the case for
connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. This result is in line with other studies which found
mismatch between spatial and temporal patterns [@adler_contrasting_2007;
@johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
that variations in space will correspond to differences of assembly stages and
then reflect the assembly/disassembly trajectories in time of communities [@].

In contrast with a meta-analysis [@soininen_relationship_2012], we found that
the evenness of abundances is positively related to the one of species
richness in space in stream fish assemblages but found no relationship in time.

This result has profound implications for conservation. As more and more
studies report community biomass and species richness trends [@hallmann_more_2017;
@ceballos_biological_2017], we documented that they might not be
equivalent in terms of consequences on the structure of the community. In
particular, the loss of the highest trophic level associated to the loss of
community biomass could of have dramatic consequences on ecosystem functioning
as highest predators are prone to stabilise communities
[@shanafelt_stability_2018; danet_species_nodate]. In contrasts, the loss of
species richness was poorly associated to modification of food-web structure,
suggesting that the species loss and gain concern lower trophic levels, which
are also in transmitting energy toward higher level of the trophic chain.

@@

Our study shows that richness and biomass temporal trends in natural fish
communities relate on different ecological processes, biomass temporal dynamics
being related to variation of highest trophic levels while it is not the case for
species richness. Our work also suggests that space for time substitution may be
relevant to predict food-web community structure in case of biomass variation
but not for species richness variation. We look forward to next investigations
to see the generality of assembly rules in food-webs. There are crucial to
better understand the temporal dynamics of food-webs structure and then its
impact on ecosystem functioning.

@@

```{r}
fig_bef_cap <- paste0(
  "Relationship between the temporal trends of community structure
  and the one of species richness. Lines correspond to the predictions of the
  linear models. The lines surrounding each point represent the standard error
  associated to the temporal trends."
)
```
```{r bef, fig.cap=fig_bef_cap}
fig1_2$rich$log_bm_std
```

```{r}
fig_bm_rich_cap <- paste0(
  "Relationship among the temporal trends of community structure
  and the one of species richness and community biomass. The lines
  surrounding each point represent the standard error associated to the temporal
  trends."
)
```
```{r bmr, out.width = "100%", fig.cap=fig_bm_rich_cap}
fig2 <- fig1_2
fig2$rich$log_bm_std <- NULL
fig2$rich <- map(fig2$rich,
  ~ .x +
    theme(axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)))
fig2$bm <- map(fig2$bm,
  ~ .x + theme(
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
)

>>>>

---
title: "Food-web temporal changes according to changes in species
richness and community biomass reveal contrasting assembly processes"
author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine (ordre non fixé)
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
  bookdown::word_document2:
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

@@

## Trends of biodiversity need to be assessed at multiple facets

@@

The documentation of biodiversity trends generally neglect species interactions
although they are fundamentals to ecosystem functioning
[@thebault_food-web_2003; oconnor_general_2016]. In food-webs, empirical and
theoretical studies reported generally that trophic level positively scales to
community biomass [@wang_biodiversity_2018; @danet_species_nodate] (add
mechanisms ?). Trophic level has also been shown to stabilise the temporal
variation of community biomass [@shanafelt_stability_2018;
@danet_species_nodate]. Connectance, which measures the degree of generalism in
a network, was shown to increase robustness to extinction [@dunne_network_2002].
However, the temporal variation of food-web structure is largely unknown
[@kortsch_disentangling_2021]. Food-web temporal variation are often reported
across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
@kaartinen_high_2012].

@@

In this line, how the temporal changes of community biomass are related to
temporal changes of species richness can still be question in natural settings,
especially in food-webs. Our knowledge on how the temporal changes of food-web
structure are related  to temporal changes in community biomass and species
richness is almost zero. Our knowledge on the relationships between food-web
structure comes often from comparison of food-web snapshots along spatial
gradient, raising the question of the validity of space for time substitution to
infer consequences of species richness and community biomass on food-web
structure. The increasing amount of availability ecological temporal series
makes possible to assess those questions. Using a standardized monitoring of
fish freshwater communities on the period 1995-2018 and a method of food-web
inference based on allometric relationships and food diet data, we assessed the
relationships among temporal changes of food-web structure, trends of community
biomass and trends in species richness. We then assessed the validity of space
for time substitution by comparing if temporal relationships display the same
patterns as spatial gradient.

@@

There was a clear relationship between the size of the communities and their
temporal dynamics. Communities that displayed low community biomass at the
beginning of their monitoring tend to display biomass increase through time
and reversely. We observed the same pattern for species richness, with
communities that displayed high species richness at the beginning of their
monitoring tend to display a decrease in species richness through time and
reversely.

@@

We modelled the dynamics the temporal trends of food-web structure ($dN$)
in function of the temporal trends of community biomass ($dB$) and species
richness ($dR$) in order to test the relationship among the temporal dynamics of network
structure from one side and species richness and community biomass from another
side.

@@

In order to control for the uncertainties of the estimated temporal trends, each
temporal trend was weighted by the inverse of the product of the standard errors of the
estimated trends, i.e. slopes for the response and the explicative
variables. We also tested a statistical model taking in account the interaction
between the temporal trends of species richness and community biomass (i.e.
adding $\beta_3dBdR$), the results are presented in supplementary material (Fig.
SXX). To model the relationships between the temporal trends of community
biomass and the one of species richness, we built equations as $dB = \alpha +
\beta_1dR + \epsilon$.

@@

To model the relationships between community biomass and species richness along
the spatial gradient, we built the equation as $B = \alpha + \beta_1R +
\beta_3E_1 + \beta_4E_2 + \epsilon$.

@@

With $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
deviation of the explicative and response variable.

@@

```{r}
class_trends_bm_rich <- rigal_classification %>%
  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
  unnest(classif) %>%
  select(variable, station, direction, acceleration, shape_class)

res_trends <- class_trends_bm_rich %>%
  filter(acceleration == "constant") %>%
  group_by(variable, direction) %>%
  summarise(n = n()) %>%
  group_by(variable) %>%
  mutate(total = sum(n), percent = round(n / sum(n) * 100))

x_var <- c("log_bm_std", "log_rich_std")
stable_st_var <- map(x_var,
  ~class_trends_bm_rich[
    class_trends_bm_rich$variable == .x &
    class_trends_bm_rich$direction == "stable",
      ]$station
)
names(stable_st_var) <- x_var

sum(stable_st_var[["log_bm_std"]] %in% stable_st_var[["log_rich_std"]] == TRUE) / length(stable_st_var[["log_bm_std"]])

sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
```

@@

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table \@ref(tab:rsq)). The spatial models were more performant, with
$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
\@ref(tab:rsq-sp)). Over the station in the dataset, we found that
`r res_trends[res_trends$variable == "log_bm_std", ]$total[1]` stations displayed monotonic trends for biomass. Among them, 
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
were classified stable,
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
decreasing,
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
increasing. Regarding the species richness, we found that
`r res_trends[res_trends$variable == "log_rich_std", ]$total[1]` stations displayed monotonic trends.
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
were classified stable,  
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
as decreasing, and 
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increasing", ]$percent`% increasing.

@@

The temporal trends of connectance was positively linked with the one of
community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), meaning also that both
temporal trends had the same direction in average. That is, the stations where
food-web connectance decreased over time had also community biomass that
decreased over time and reversely. It means that communities that lose biomass
over time, also loses generalist predators and reversely that communities
gaining biomass over time also gain generalist predators. Spatially, we found
also a positive relationship between median connectance and median species
richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
significant relationships between the temporal trends of connectance and the one
of species richness (Fig. \@ref(fig:bmr)D) when we found spatially a stong
negative relationship between median connectance and median species richness
($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).

@@

Spatially and temporally, species richness scaled positively with community
biomass. Spatially, this result is in accordance with numerous studies was
already found in streams [@woods_testing_2020; @danet_species_nodate] but also
in grasslands, salt marches and forests [@hector_plant_1999;
@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
works also in time in food-webs. The positive relationship between species
richness and total biomass might be due to positive complementarity in resource
use [@carey_determining_2011], which is held by niche differentiation
[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
probability of getting high biomass species with higher species richness
[@loreau_biodiversity_2001].

## Biomass and species richness temporal trends relies on different assembly rules

While we found a strong relationship between the temporal trends of community
biomass and the one of species richness, our results suggest that temporal trends in
community biomass and species richness have highly different consequences on the
structure of food-webs. Indeed, temporal trends of connectance and average
trophic level was positively associated to the one of community biomass while no
significant association was found with temporal trends of species richness.
Moreover, biomass evenness temporal trends was negatively associated to temporal
trends of community biomass whereas positively associated to temporal trends of
species richness. All together, it suggests that temporal trends of biomass and
species richness indicates different food-webs assembly processes.

The temporal trends of connectance was positively linked to that one of
community biomass, meaning that connectance increases through time in a given
site when community biomass increases through time and reversely that
connectance decreased in food-webs where community biomass decreased through
time. It suggests that community biomass losses are linked to the generalist
predators while gains in community biomass are associated to the higher presence
of generalist predators. This interpretation is in line with (2) the results
that community biomass losses through time were associated to a temporal
decrease of average trophic level and that community biomass temporal gains were
associated to temporal increase of average trophic level. Another piece of
evidence is that evenness of biomass, measured by the pielou, decreased through
time as community biomass increased, meaning that biomass distribution across
species become less even when community biomass decreased. Reversely, in
food-webs that displayed temporal decrease in community biomass, we found that
evenness of biomass increased, i.e. that biomass distribution across species
become more even. Because predators-preys interactions relates in part on
bodysize and thus bodymass in part, we may expect that a given gain in higher
predators leads to a decrease of biomass evenness and reversely. In the same
line, the temporal trends of community biomass were positively correlated to the
temporal trends of the number and proportion of piscivorous trophic species
present in the community (Fig. SXX).

In contrast, we found temporal trends of connectance and average trophic level
were not related to the temporal trends of species richess. However, we found
that temporal trends of the number of piscivorous species and piscivorous
trophic species were strongly positively linked to the temporal trends of
species richness (Fig. S3). It suggests that the temporal decrease of species
richness that we observed in our data are concomimant to simultaneous losses of
piscivorous and non-piscivorous species that leads to the absence of temporal
trend in connectance and average trophic level and symmetrically for the
temporal increase of species richness. Furthemore, we found that the temporal
trends of biomass evenness had a positive relationship with the one of species
richness, the opposite of what we found for temporal trends of community biomass.
Together with the fact that species richness temporal trends had a positive
relationship with the temporal trends of community biomass, it suggests that the
species richness temporal trends are linked to gain or loss of redundancy in
food-webs without a clear signature in the vertical structure of the food-webs.

@@

In time and along spatial gradient, we found that connectance was positively
linked to community biomass. This result is also in accordance with theoretical
work showing that higher food-web connectance can result in higher community
biomass [@thebault_food-web_2003], but other display negative relationship
[@poisot_trophic_2013], highlighting that the relation between connectance and
community biomass may be dependant of assembly processes at work.]. In the same
line, we found that average trophic level had a positive relationship with
community biomass in space and time. It is in accordance with a theoretical
model showing that the presence of higher predators can lead to higher community
biomass [@wang_biodiversity_2018].  We also found in space and time that
evenness of biomass was negatively related to community biomass. This result is
in accordance with the observation of top-heavy shape of biomass pyramids in
food-webs, particularly in freshwater systems [@mccauley_prevalence_2018]. Many
mechanisms can be responsible have been invoked to explain this pattern but
omnivory, which is present in most of piscivorous species in our dataset, may
favor this shape by increasing food transfer efficiency toward higher trophic
level.

Surprisingly, we found that the temporal trends of connectance was not related
to the one of species richness as found spatially in most empirical food-web
[@dunne_network_2006] and also in the present study. We explained this pattern
by the fact that the temporal variation of species richness in our dataset seems
to be linked to variation in the level of redundancy in the role in the
food-webs rather than overall change of the vertical structure of food-webs. The
same rational can applied with average trophic level. *This discrependacy might
be due to the crucial assumptions that variations in space will correspond to
differences of assembly stages and then reflect the assembly/disassembly
trajectories in time of communities. Temporal variation of species richness
might relate on transitory dynamics while spatial gradient reflect aggregated
dynamics over longer time scale including a far number of processes including
high species turnover along spatial gradient.* This result is in line with other
studies which found mismatch between spatial and temporal patterns
[@adler_contrasting_2007; @johnson_testing_2008].  
However, we found agreement between space and time analysis for the positive
relationship between evenness of biomass and species richness. Another reason
might be that the spatial gradient displays a higher range of variation for
species richness than the temporal stations (Fig. S2). However, it might not
explain why we found strong relationships between the temporal trend of species
richness from one side and the temporal trends of community biomass, biomass
evenness, the number of piscivore species (Fig. S3). *No more idea, need
coffee*.

However, our result that food-web structure does not change a lot with temporal
variation of species richness is in line with the insurance hypothesis
[@yachi_biodiversity_1999]. In this view, the temporal loss and gain of species
richness represent respectively loss and gain of redundancy in the
food-web structure. Our results have profound implications for conservation. As
more and more studies reported community biomass and species richness trends
[@hallmann_more_2017; @ceballos_biological_2017], we documented that they might
not be equivalent in terms of consequences on the structure of the community. In
particular, the loss of the highest trophic level associated to the loss of
community biomass could have dramatic consequences on ecosystem functioning
as the highest predators are prone to stabilise communities
[@shanafelt_stability_2018; @danet_species_nodate]. In contrasts, the loss of
species richness might be linked to loss of redundancy in the food-web,
highlighting that those communities may become more at risk regarding future
perturbations [@yachi_biodiversity_1999]. Overall, it suggests that monitoring
several facets of biodiversity is essential to infer how ecological communities
are reshaped by loss and gain of biomass and species richness.

We further found that most temporal trends of food-webs were classified as
stable for species richness and community biomass. We found almost the same
number of stations that displayed temporal decrease or increase for species
richness, and twice more stations displayed decrease in community biomass than
increase. While, the spatial coverage of our data is good, it would be rather
risky to conclude about biodiversity trends in freshwater fish communities in
France. Mainly because we did not assess pressures that may affect
the temporal trends such as land-use changes and species invasions
[@comte_climate_2021; @su_human_2021].

@@

Our study suggests that richness and biomass temporal trends in natural fish
communities relate on different ecological processes, biomass temporal dynamics
being related to variations of at highest trophic levels while species richness
impacts redundancy of food-web structure. Our result also suggests that space
for time substitution may be relevant to predict the effects of community
biomass losses or gains on food-web structure. However, it might not the case
for species richness temporal variation. We look forward to next investigations
to see the generality of assembly rules in food-webs. There are crucial to
better understand the temporal dynamics of food-web structure and then its
impact on ecosystem functioning.

@@

```{r}
fig_bef_cap <- paste0(
  "Relationship between the temporal trends of community structure
  and the one of species richness. Lines correspond to the predictions of the
  linear models. The lines surrounding each point represent the standard error
  associated to the temporal trends."
)
```
```{r bef, fig.cap=fig_bef_cap}
ggMarginal(fig1_2$rich$log_bm_std, type = "histogram")
```

```{r}
fig_bm_rich_cap <- paste0(
  "Relationship among the temporal trends of community structure
  and the one of species richness and community biomass. The lines
  surrounding each point represent the standard error associated to the temporal
  trends."
)
```
```{r bmr, out.width = "100%", fig.cap=fig_bm_rich_cap}
library(ggExtra)
fig2 <- fig1_2
fig2$rich$log_bm_std <- NULL
fig2$rich <- map(fig2$rich,
  ~ .x +
    theme(axis.text = element_text(size = 6),
    axis.title = element_text(size = 8))
  )
fig2$bm <- map(fig2$bm,
  ~ .x + theme(
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    )
)

# Add histograms
fig2$bm <- map(fig2$bm,~ggMarginal(.x, type = "histogram"))
fig2$rich <- map(fig2$rich,~ggMarginal(.x, type = "histogram"))
